---
title: "Child Parent interaction in Korea"
author : "Seewoo Li"
date : "2020-06-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r prep, include=FALSE}
library(readr)
library(tidyverse)
library(skimr)
library(stringr)
library(recipes)
library(tidymodels)
library(VGAM)
setwd("C:/Users/CU/Desktop/blogdown/blog2/content/post")
KoreaData <- read_csv('KoreaData.csv')
```
# 1. Introduction
* The data is collected from [PISA(Programme for International Student Assessment)](https://www.oecd.org/pisa/data/2018database/).
* Country: Korea 
* Students' age: HighSchool 1^st^Grade
* A fosterer has responded to several questionnaire. And this report analyzes data obtained from those questionnaire.
* Explanation of variables
  + Early : Child regularly attended prior to <grade 1 in ISCED 1>: Early childhood educational development [...]
  0: No, 1: Yes
  + Care : <the last academic year>, participation hindered: I had no one to take care of my child/ children.
  0: There was no one, 1: There was someone
  + Parent : Who will complete this questionnaire?
  0: Father, 1: Mother
  + Talk : Activities with your child, how often: Spend time just talking to my child
  1: Never or hardly ever
  2: Once or twice a year
  3: Once or twice a month
  4: Once or twice a week
  5: Every day or almost every day
  + Lastly, this report is to analyze the relationship among _'Talk'_, _'Early'_, _'Care'_, _'Parent'_.

# 2. Eploratory Data Analysis
```{r, include=FALSE}
rdata <- KoreaData %>%
  select(CNTSTUID,
         PA018Q02NA,
         PA009Q03NA,
         PA001Q01TA,
         PA001Q02TA,
         PA001Q03TA,
         PA003Q03TA) %>%
  filter(PA018Q02NA != 'NA' &
         PA009Q03NA != 'NA' &
         PA001Q01TA != 'NA' &
         PA001Q02TA != 'NA' &
         PA001Q03TA != 'NA' &
         PA003Q03TA != 'NA' )
#skim(rdata)
colnames(rdata) <- c('ID', 'Early', 'Care', 'Mother', 'Father', 'Other', 'Talk')
rdata <- rdata %>% 
  mutate(Early = recode(Early, '1'=1L, '2'=0L),
         Care = Care-1,
         Parent = Mother + 2*Father + 3*Other,
         Parent_drop = Mother + Father + Other,
         Day = if_else(Talk == 5, 1, 0),
         Week = if_else(Talk == 4, 1, 0),
         Month = if_else(Talk == 3, 1, 0),
         Year = if_else(Talk == 2, 1, 0),
         Never = if_else(Talk == 1, 1, 0))%>%
  filter(Parent_drop == 1)%>%
  filter(Parent != 3) %>%
  mutate(Parent = recode(Parent, '1'=1L, '2'=0L)) %>%
  select(-Parent_drop, -Mother, -Father, -Other, -ID)
```
```{r, echo=FALSE}
#skim(rdata)
```
```{r, echo=FALSE, message=FALSE}
tbl <- full_join(count(rdata, Early),
          count(rdata, Care)) %>%
full_join(., count(rdata, Parent)) %>%
full_join(., count(rdata, Talk))
tbl %>% select(!n, n)
```

***
# 3. Selecting Model
### Proportional and Unproportional
```{r}
fit1 <- vglm(cbind(Never, Year, Month, Week, Day)~ Early + Care + Parent, 
             family = cumulative(parallel = TRUE), data = rdata)
fit2 <- vglm(cbind(Never, Year, Month, Week, Day)~ Early + Care + Parent, 
             family = cumulative(parallel = FALSE), data = rdata)
```
```{r, include=FALSE}
summary(fit1)
summary(fit2)
```
 \(\Delta\chi^2=Deviance_{proportional}-Deviance_{unproportional}\) = 11061.27-11051.1=`r 11061.27-11051.1`
 \(df=df_{proportional}-df_{unproportional}\) = 21565-21556=`r 21565-21556`
 \(\chi^2_{.05}(9)\) = `r qchisq(.95, 9)`
 Since `r qchisq(.95, 9)` > `r 11061.27-11051.1`, choose proportional model.

### Dropping 'Early'
```{r}
fit_without_Early <- vglm(cbind(Never, Year, Month, Week, Day)~ Care + Parent,
                          family = cumulative(parallel = TRUE), data = rdata)
```
```{r, include=FALSE}
summary(fit_without_Early)
```
 \(\Delta\chi^2=Deviance_{without Early}-Deviance_{proportional}\) = 11061.35-11061.27=`r 11061.35-11061.27`
 \(df=df_{without Early}-df_{proportional}\) = 21566-21565=`r 21566-21565`
 \(\chi^2_{.05}(1)\) = `r qchisq(.95, 1)`
 Since `r qchisq(.95, 1)` > `r 11061.35-11061.27`, choose model without 'Early'.
```{r, include=F}
#fit3 <- vglm(cbind(Never, Year, Month, Week, Day)~ Early * Care * Parent, family = cumulative(parallel = F), data = rdata)
#fit4 <- vglm(cbind(Never, Year, Month, Week, Day)~ 1, family = cumulative(parallel = FALSE), data = rdata)
#summary(fit3)
#summary(fit4)
```
*** 
# 4. Model
* Model : 

\[logit{P(Y_{Talk}\le j)}=\alpha_j+\beta_1X_{Care}+\beta_2X_{Parent}\]
 
That is,
 $logit{P(Y_{Talk}\le j)}=\alpha_j-0.35023X_{Care}-0.80328X_{Parent},$
 $where  \alpha_{Never}= -4.22657, \alpha_{Year}= -3.11453, \alpha_{Month}= -1.02188, \alpha_{Week}= 1.13272 .$

Since $\beta_1<0$, when there is someone to take care of the child(i.e., $X_{Care}=1$), 
$p(having more time to talk)$ increases.

Since $\beta_2<0$, when the mother of the child responded to the questionnaire(i.e., $X_{Parent}=1$), 
$p(having more time to talk)$ increases.

***
# 5. Discussion
The result implies that the exsistence of child care which is indicated by _Care_ is related to child-parent interaction, and implies that gender of the respondent of the questionnaire which is indicated by _Parent_ is related to child-parent interaction. It is suggested that further study should be conducted for discovering the reasons that why only `r 678/4706`% of the respondents responded that there is no one to take care of their child and why only `r 828/4565`% of the respondents was father.





