---
title: "-Data-Analysis-Investigating-Relationships-Between-Variables"
author: "Seewoo Li"
date: '2020-04-21T22:00:00+09:00'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Selecting Model

### 1. Making Table
```{r, echo=FALSE}
freq <- c(14,483,497,1008,1105,411111,4624,157342)
S <- c(1,1,0,0,1,1,0,0)
E <- c(1,0,1,0,1,0,1,0)
I <- c(1,1,1,1,0,0,0,0)

tab <- data.frame(freq, S, E, I)
tab
```

### 2. Fitting All Possible Models
```{r}
fit1 <- glm(freq~S*E*I, family=poisson(link='log'), data=tab)
fit2 <- glm(freq~S+E+I+S:E+S:I+E:I, family=poisson(link='log'), data=tab)
fit3 <- glm(freq~S+E+I+S:E+S:I, family=poisson(link='log'), data=tab)
fit4 <- glm(freq~S+E+I+S:E+E:I, family=poisson(link='log'), data=tab)
fit5 <- glm(freq~S+E+I+S:I+E:I, family=poisson(link='log'), data=tab)
fit6 <- glm(freq~S+E+I+S:E, family=poisson(link='log'), data=tab)
fit7 <- glm(freq~S+E+I+S:I, family=poisson(link='log'), data=tab)
fit8 <- glm(freq~S+E+I+E:I, family=poisson(link='log'), data=tab)
fit9 <- glm(freq~S+E+I, family=poisson(link='log'), data=tab)
```

### 3. Deviance and AIC for Selecting the Best Model
```{r, echo=T}
devi <- c()
aic <- c()
for(i in 1:9){
  devi[i] <- round(eval(parse(text=paste('fit',i,'$deviance', sep=''))),2)
  aic[i] <- round(eval(parse(text=paste('fit',i,'$aic', sep=''))),2)
}
model <- c('saturated','homogeneous', 'SE_SI', 'SE_EI', 'SI_EI', 'SE', 'SI', 'EI','Mutual indep')
model_selec <- cbind(model, devi, aic)
model_selec
```


### 4. Model Selection
* Although **saturated model** has the least AIC among others, it is possible for the model which has **homogeneous association** being selected for the convenience in interpretation.
* The increment of deviance by 2.85 can be accepted in return for the decrement of degrees of freedom by 1.
\[Model : log{\mu_{ijk}}=\lambda+\lambda_i^S+\lambda_j^E+\lambda_k^I+\lambda_{ij}^{SE}+\lambda_{ik}^{SI}+\lambda_{jk}^{EI}\]


# Interpretation

* The model has *homogeneous association*.$
* $log{OddsRatio_{SE(k)}}=log{\frac{\mu_{11(k)}\mu_{00(k)}}{\mu_{10(k)}\mu_{01(k)}}}=\lambda_{11}^{SE}$, for all k=0,1
* $log{OddsRatio_{SI(j)}}=log{\frac{\mu_{1(j)1}\mu_{0(j)0}}{\mu_{1(j)0}\mu_{0(j)1}}}=\lambda_{11}^{SI}$, for all j=0,1
* $log{OddsRatio_{EI(i)}}=log{\frac{\mu_{(i)11}\mu_{(i)00}}{\mu_{(i)10}\mu_{(i)01}}}=\lambda_{11}^{EI}$, for all i=0,1
* Each pair of variables S, E, I is not independent, but its relation is not affected by *the* leftover.

